tower-insitu

### 2024-08-26 examples/tower-insitu.Rmd
add tower-insitu examples and articles

---
title: "surface-insitu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{surface-insitu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "surface-insitu"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_surfaceinsitu.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfacetinsitu.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_surfaceinsitu_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfaceinsitu_map.png?raw=true)

>>>>

---
title: "tower-insitu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tower-insitu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "tower-insitu"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_towerinsitu.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_towerinsitu.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_towerinsitu_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_towerinsitu_map.png?raw=true)
